### 2023-03-08 manuscript.tex
Adding librsvg v.2.52.5 to correctly export SVG files to DOCX [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366847805

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f2068e319930774a03f19646dc6c571d617a9f34/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f2068e319930774a03f19646dc6c571d617a9f34}{SORTEE-Github-Hackathon/manuscript@f2068e3}
on March 8, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b}{SORTEE-Github-Hackathon/manuscript@cd23484}
on March 8, 2023.
